---
title: "data_prep_flow"
author: "yarden"
date: "March 5, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
First let's present our raw data on bike trips (taken from Big Query)
```{r}
raw_data_trips = read.csv("C:\\Users\\User\\Dropbox\\IDC\\Courses\\BusinessAnalytics\\project\\bike\\dataSets\\raw_data\\bikeshare_trips_full.csv", header=TRUE, as.is=TRUE, na.strings=c("NA", ".", ""))
str(raw_data_trips)
```
And let's present our raw data on bike stations (taken from Big Query)
```{r}
raw_data_stations = read.csv("C:\\Users\\User\\Dropbox\\IDC\\Courses\\BusinessAnalytics\\project\\bike\\dataSets\\raw_data\\bikeshare_stations_full.csv", header=TRUE, as.is=TRUE, na.strings=c("NA", ".", ""))
str(raw_data_stations)
```

Now let's present our raw data for San Francisco Bay Area (merge of the two above)
```{r}
raw_data_sanFran = read.csv("C:\\Users\\User\\Dropbox\\IDC\\Courses\\BusinessAnalytics\\project\\bike\\dataSets\\san_francisco_data\\sanFran_full.csv", as.is = TRUE)
str(raw_data_sanFran[-c(1,2)])
```

Set dates, duration & add columns of day, month, year, weekend, hour
(from data_preprocessing.R)
```{r}
train_improved = read.csv("C:\\Users\\User\\Dropbox\\IDC\\Courses\\BusinessAnalytics\\project\\bike\\dataSets\\san_francisco_data\\sanFran_train_extended.csv", as.is = TRUE)
train_improved = train_improved[-c(1,2)]
test_improved = read.csv("C:\\Users\\User\\Dropbox\\IDC\\Courses\\BusinessAnalytics\\project\\bike\\dataSets\\san_francisco_data\\sanFran_test_extended.csv", as.is = TRUE)
test_improved = test_improved[-c(1,2,3,25)]
improved_data = rbind(train_improved,test_improved)
str(improved_data)
```

Add minimum distances between each station to transportation interest points (bart, calltrain, ferry)
(from Script1.R)
```{r}
train_improved1 = read.csv("C:\\Users\\User\\Dropbox\\IDC\\Courses\\BusinessAnalytics\\project\\bike\\scriptsFlowR\\dataSets\\train4tree_withPrediction_num.csv", as.is = TRUE)
test_improved1 = read.csv("C:\\Users\\User\\Dropbox\\IDC\\Courses\\BusinessAnalytics\\project\\bike\\scriptsFlowR\\dataSets\\test4tree_withPrediction_num.csv", as.is = TRUE)
data_withTransport = rbind(train_improved1,test_improved1)
str(data_withTransport)
```

Convert end-station locations to UTM coordinate system
(from Script2.R)
```{r}
train_improved2 = read.csv("C:\\Users\\User\\Dropbox\\IDC\\Courses\\BusinessAnalytics\\project\\bike\\scriptsFlowR\\dataSets\\trainUTM.csv", as.is = TRUE)
test_improved2 = read.csv("C:\\Users\\User\\Dropbox\\IDC\\Courses\\BusinessAnalytics\\project\\bike\\scriptsFlowR\\dataSets\\testUTM.csv", as.is = TRUE)
data_UTM = rbind(train_improved2,test_improved2)
str(data_UTM)
```

Filter data to 2016 & suscribers with legal zip code only
(from Script3.R)
```{r}
train = read.csv("C:\\Users\\User\\Dropbox\\IDC\\Courses\\BusinessAnalytics\\project\\bike\\scriptsFlowR\\dataSets\\trainSuscribers2016_4RT1.csv", as.is = TRUE)
test = read.csv("C:\\Users\\User\\Dropbox\\IDC\\Courses\\BusinessAnalytics\\project\\bike\\scriptsFlowR\\dataSets\\testSuscribers2016_4RT1.csv", as.is = TRUE)
data_2016 = rbind(train,test)
str(data_2016)
```